---
title: "Markdown_W1Live"
output: html_document
date: "2024-08-29"
---

#### Read the dataset and check some of its basic information:
```{r}
WV = read.csv("WorldValues_W1Live.csv")
dim(WV) #Dimension of the dataset
head(WV) #First few rows of the dataset
class(WV) #Class type of the data object
str(WV) #Variable types
```

#### 1: Does this dataset have missing values? If so, how many missing values does it have?
```{r}
anyNA(WV)
sum(is.na(WV))
```

#### 2: Create an object that contains unique birth years. How many unique birth years the dataset have?
```{r}
unique(WV$BirthYear)
length(unique(WV$BirthYear))
```


#### 3: Create a new variable that stores the age of each respondent at the time of the survey. (add this variable to the dataset)
```{r}
WV$Age = WV$SurveyYear - WV$BirthYear


```


#### 4: What is the average age of survey respondents?
```{r}


```


#### 5: How many responses are from country 12? The variable 'Code' captures country code for responses.
```{r}

```

#### 6: What is the average age of respondents from country 12?
```{r}

```


